Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-30 paper.tex
Edit Participants and Trading Model

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream.

\subsubsection{Consumer}
Consumers aspire to obtain IoT data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the IoT data from data providers.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}. Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption. Then the broker provides the matching service for data provider’s products and consumer’s queries. After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel.

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$. Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.

@@

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

>>>>

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream. They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their sensors.

\subsubsection{Consumer}
Consumers aspire to obtain IoT data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the IoT data from data providers. They search products on the marketplace and pay for subscription fee. While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically. The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains sensing data.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}. Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption. Then the broker provides the matching service for data provider’s products and consumer’s queries. After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel. For each products, brokerage fees will be charged by the broker.

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

The data provider requests the consumers list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.

Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.

@@

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:
